\section{Related Work}

\subsection{Brain-Inspired Perception}
\hspace{1pc}The human visual cortex possesses remarkable environmental perception capabilities, serving as a crucial component of the central nervous system and responsible for transforming visual signals into comprehensible information \cite{9134376}. 
Traditional visual encoding models are limited by the use of either handcrafted or deep learning features merely, despite their individual advantages\cite{kubilius2019brain}. 
To integrate the two, Cui et al. \cite{8574054} proposed the GaborNet-VE model, which combines Gabor features with deep learning to form an efficient visual encoding framework. 
However, this model requires significant parameter adjustments across different tasks, and the interpretability of its deep learning component remains inadequate\cite{liao2021statistical}. 
In contrast, our proposed BID model demonstrates outstanding performance in revealing decision-making mechanisms and exhibiting strong generalization capabilities.

\subsection{Brain-Inspired Decision}
\hspace{1pc}In practical environments, agents often need to handle continuous state spaces, while traditional reinforcement learning models, such as Q learning methods, are more fit to discrete states\cite{xi2020automatic}. 
To address this issue, Zhao et al. \cite{zhao2018brain} proposed the prefrontal cortex and basal ganglia method, which subdivides continuous states and utilizes a continuous function to capture temporal reward. 
However, the design of continuous reward functions remains a challenge. 
In non-Gaussian and nonlinear environments, traditional methods struggle to cope with their nonlinear and non-Gaussian characteristics\cite{naghshvarianjahromi2020natural}. 
Inspired by human decision-making in brain, some researchers~\cite{dai2013dynamic} designed an autonomous computation layer accroding to a cognitive dynamic system (CDS), providing agents in NGNLE with stronger decision-making capabilities. 
Although these methods attempt to mimic the decision-making process of the human brain, structural differences lead to a lack of transparency in their processes. 
Therefore, it is crucial to construct a network architecture that align with the anatomical structure of human brain.


